%% \documentclass[11pt, letterpaper]{awesome-cv}
\usepackage{paracol}
\usepackage{progressbar}
\geometry{left=1cm, top=.8cm, right=1cm, bottom=1cm, footskip=.5cm}
\fontdir[fonts/]

%TODO Not sure if I like the highlighting or not
%% \setbool{acvSectionColorHighlight}{false}

% Available options: circle|rectangle,edge/noedge,left/right
%% \photo[edge,right]{filename}

\renewcommand{\acvSectionTopSkip}{1mm}
\progressbarchange{ticksheight=0}

\name{Michael}{Mrozek}
\position{Software Engineer}
\email{resume@mrozekma.com}
\homepage{cv.mrozekma.com}
\github{mrozekma}
\gitlab{mrozekma}
\stackoverflow{309308}{Michael Mrozek}

\begin{document}
\makecvheader[R]

\makecvfooter{Generated \today. Unabridged version available from \href{http://cv.mrozekma.com/}{http://cv.mrozekma.com/}}{}{\thepage}

\untagged{technical-skills,experience,education,projects,publications}{
	\centering
	\vfill
	No sections requested\ldots
	\vfill
}

\iffalse
\cvsection{Tags}
\begin{cvparagraph}
\begin{itemize}[leftmargin=2ex, nosep, noitemsep]
\item background: \iftagged{background}{yes}{no}
\item technical-skills: \iftagged{technical-skills}{yes}{no}
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
    \item languages: \iftagged{languages}{yes}{no}
    \item certifications: \iftagged{certifications}{yes}{no}
    \end{itemize}
\item experience: \iftagged{experience}{yes}{no}
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
    \item mercury: \iftagged{mercury}{yes}{no}
    \item microsemi: \iftagged{microsemi}{yes}{no}
    \item arxan-defense-systems: \iftagged{arxan-defense-systems}{yes}{no}
    \item arxan: \iftagged{arxan}{yes}{no}
    \item rose-hulman: \iftagged{rose-hulman}{yes}{no}
    \item ventures: \iftagged{ventures}{yes}{no}
    \item perry-schools: \iftagged{perry-schools}{yes}{no}
    \item perritech: \iftagged{perritech}{yes}{no}
    \end{itemize}
\item education: \iftagged{education}{yes}{no}
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
    \item masters: \iftagged{masters}{yes}{no}
    \item bachelors: \iftagged{bachelors}{yes}{no}
    \item high-school: \iftagged{high-school}{yes}{no}
    \end{itemize}
\item projects: \iftagged{projects}{yes}{no}
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
    \item sprint: \iftagged{sprint}{yes}{no}
    \item noisebot: \iftagged{noisebot}{yes}{no}
    \item spades: \iftagged{spades}{yes}{no}
    \item got: \iftagged{got}{yes}{no}
    \item lync-helper: \iftagged{lync-helper}{yes}{no}
    \item gir: \iftagged{gir}{yes}{no}
    \item woop: \iftagged{woop}{yes}{no}
    \end{itemize}
\item publications: \iftagged{publications}{yes}{no}
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
    \item subverting-the-fundamentals-sequence: \iftagged{subverting-the-fundamentals-sequence}{yes}{no}
    \end{itemize}
\end{itemize}
\end{cvparagraph}
\fi

\begin{taggedblock}{technical-skills}
\cvsection{Technical Skills}

\newcommand{\languages}{
	\cvsubsection{Languages}

	\begin{cvparagraph}
	\skill{.9}{Extensive experience with C++, Java, Python, and shell scripting.}
	\skill{.6}{Experience with PHP and C\#. Desperate for more C\# opportunities.}
	\skill{.5}{Experience with SQL and miscellaneous databases, including MySQL, MariaDB, PostgreSQL, and Redis.}
	\end{cvparagraph}
}
\newcommand{\tools}{
	\cvsubsection{Tools and Frameworks}

	\begin{cvparagraph}
	\skill{.9}{Extensive experience with Git. Some experience with Subversion.}
	\skill{.9}{Extensive experience with Linux and Windows (through 10).}
	\skill{.8}{Extensive experience with the Atlassian toolset, including Jira, Bitbucket, and Confluence.}
	\skill{.7}{Experience with jQuery.}
	\skill{.5}{Experience creating GUIs in JavaFX and Qt.}
	\end{cvparagraph}
}

% bothSkillsSections = languages && tools-and-frameworks
\newbool{bothSkillsSections}
\setbool{bothSkillsSections}{false}
\tagged{languages}{\tagged{tools-and-frameworks}{\setbool{bothSkillsSections}{true}}}

% if(languages && tools-and-frameworks)
\ifbool{bothSkillsSections}{
	% Display the sections side by side
	\newcommand{\skill}[2]{
		\progressbar[width=3em]{#1}~~~\parbox[t]{.43\textwidth}{#2}\\
	}
	\begin{paracol}{2}
	\languages
	\switchcolumn
	\tools
	\end{paracol}
}{
	\newcommand{\skill}[2]{
		\progressbar{#1}~~~#2\\
	}
	\tagged{languages}{\languages}
	\tagged{tools-and-frameworks}{\tools}
}

\vspace{-30pt} % Way too much space after the previous section
\end{taggedblock}

\begin{taggedblock}{experience}
\cvsection{Experience}
% \work{Tag}{Company}{Title}{When}{Content}
\newcommand{\work}[5]{
	\tagged{#1}{\cventry{#3}{#2}{#4}{}{
		\begin{cvitems}
		#5
		\end{cvitems}
	}}
}
\begin{cventries}
\work{mercury}{Mercury}{Software Development Engineer}{2016 - Present}{
	\item Designed and rolled out an automated build and test system for a number of projects.
	\item Handled the office migration to Atlassian tools, including moving all projects from Subversion to Bitbucket.
		\begin{itemize}[leftmargin=3ex, nosep, noitemsep]
		\item Implemented a tool to manage cross-repository dependencies in Bitbucket, and an addon to track additional project information within Bitbucket.
		\end{itemize}
	\item Fully automated a recurring task needed by a customer, so it can now be done on demand in about 90 minutes
	\item Fixed and redesigned large portions of an embedded system of interconnected Microblaze cores used by many customers
}%

\work{microsemi}{Microsemi}{Software Developer}{2010 - 2016}{
	\item Implemented and improved miscellaneous whitebox cryptography algorithms, including RSA, AES, and elliptic curve DSA.
	\item Developed an OpenSSL engine wrapping our whitebox cryptography implementations so they could be used by any application wrapping OpenSSL.
	\item Implemented the security model and key management policy for an Android password manager.
	\item Designed and implemented multiple higher level protocols wrapping existing whitebox cryptography to satisfy customer needs.
	\item Red- and blue-teamed several devices, finding a number of vulnerabilities. Wrote large portions of the final reports detailing the vulnerabilities, their severity, and potential mitigations and fixes.
}%

\work{arxan-defense-systems}{Arxan Defense Systems}{Software Security Analyst}{2009 - 2010}{
	\item Implemented many features in CodeSEAL, a product that analyzes executables and modifies them to protect against reverse engineering or modification.
	\item Developed WhiteboxRSA, an RSA implementation that hides the key to frustrate recovery even when the implementation is under an attacker's control.
}%

\work{arxan}{Arxan}{Intern}{2008 - 2009}{
	\item Engineering intern on a team that developed TransformIT, a white box cryptography solution.
	\item Subsequently accepted an opportunity to continue work remotely during the school year before transitioning to full-time employment after graduation.
}%

\work{ventures}{Ventures}{Team Lead}{2007 - 2008}{
	\item Head of a team of students that specified, designed, developed and launched the web portal for a promising online startup company.
	\item Handled maintenance of development servers and software.
	\item Maintained source code repository and bug tracking system.
	\item Reviewed code produced by other team members.
}%

\work{rose-hulman}{Rose-Hulman}{Teaching Assistant, CSSE Newsletter Editor}{2005 - 2008}{
	\item Assisted students in many introductory programming classes with fundamental object-oriented techniques, UML, project planning, and completing team-based goals.
	\item Responsible for all phases of the CSSE newsletter production, from writing to publishing.
}%

\work{perry-schools}{Perry Schools}{Website Designer, Technician, Database Administrator}{2001 - 2007}{
	\item Project coordinator that designed and implemented a completely new look and feel for the school district's 5000+ page website, including a custom CMS and DB design.
	\item Converted all existing webpages to a new format and implemented a new, more efficient interface.
	\item Designed, implemented, and maintained the school's first online course registration system.
}%

\work{perritech}{Perritech}{President, Technician}{2001 - 2005}{
	\item Recruited in 2001 as a computer technician, responsible for the 2000+ computer network.
	\item Subcontracted to various local businesses for programming, website design, networking and system administration.
	\item Promoted to President in 2005, managing four directors and a number of technicians.
	\item Spearheaded a presentation at the Ohio State SchoolNet Convention illustrating the benefits of a student-run technology company fully executed within a school district. Subsequently invited to Seoul, Korea for the 6th Global Forum to make a detailed presentation on how to duplicate our success throughout many school districts.
}
\end{cventries}
\vspace{-5pt}
\end{taggedblock}

\begin{taggedblock}{education}
\cvsection{Education}
% \school{Tag}{School}{Degree}{Location}{When}{Content}
\newcommand{\school}[6]{
	\tagged{#1}{\cventry{#3}{#2}{#4}{#5}{
		#6
	}}
}

\begin{cventries}
\school{masters}{Purdue University}{MS Computer Science}{West Lafayette, IN}{May 2015}{
	Cumulative GPA: 3.67
}%

\school{bachelors}{Rose-Hulman Institute of Technology}{BS Computer Science, Software Engineering (Cum Laude)}{Terre Haute, IN}{May 2009}{
	\makebox[2in][l]{Cumulative GPA: 3.48} Upperclass GPA: 3.70
}%

\school{high-school}{Perry High School}{Graduate with Honors}{Perry, OH}{May 2005}{
	\makebox[2in][l]{AP Computer Science -- 5} National AP Scholar with Distinction
}%
\end{cventries}
\vspace{-5pt}
\end{taggedblock}

\begin{taggedblock}{projects}
\cvsection{Projects}
\newcounter{projectColSplit}
% \project{Tag}{Name}{Repo URL}{Content}
\newcommand{\project}[4]{
	\tagged{#1}{
		\cvsubsection{#2} \href{#3}{\faGithubSquare}

		\begin{cvparagraph}
		#4
		\end{cvparagraph}

		\stepcounter{projectColSplit}
		\ifnum\the\value{projectColSplit}=2
		\setcounter{projectColSplit}{0}
		\switchcolumn
		\fi
	}
}

\begin{paracol}{3}
\project{sprint}{Sprint}{https://github.com/mrozekma/sprint}{
	A web-based Scrum tracking tool tailor-made for our project needs at Microsemi. Now used at several other companies.
}

\project{noisebot}{Noisebot}{https://github.com/mrozekma/noisebot}{
	An IRC/Slack chat bot that supports reloadable modules and easy modification by end-users.
}

\project{spades}{Spades}{https://github.com/mrozekma/spades}{
	A web-based view of an IRC-hosted Spades card game. Offers a convenient view of the current game state, previous hands, and even past games.
}

\project{got}{Got}{https://github.com/mrozekma/got}{
	A command-line application to automatically download and track Git repositories. Intended to faciliate dependency resolution.
}

\project{lync-helper}{Lync Helper}{https://gitlab.com/mrozekma/lynchelper}{
	A GUI for sharing code over an office chat network. Supports syntax highlighting. Also logs conversations to text files on disk.
}

\project{gir}{Gir}{https://github.com/mrozekma/gir}{
	An ncurses editors for git interactive rebase files, which are normally edited in a regular text editor.
}

\project{woop}{Woop}{}{
	A webkit-based web browser with vim-style keybindings and modes.
}
\end{paracol}
\vspace{-20pt} % Way too much space after the previous section
\end{taggedblock}

\begin{taggedblock}{publications}
\cvsection{Publications}

\tagged{subverting-the-fundamentals-sequence}{
	\begin{cvparagraph}
	Clifton, C., Kaczmarczyk, L.C., Mrozek, M. ``Subverting the Fundamentals Sequence: Using Version Control to Enhance Course Management''.\\
	Presented at the 38\textsuperscript{th} Annual Technical Symposium on Computer Science Education (SIGCSE 2007).
	\end{cvparagraph}
}
\end{taggedblock}

\end{document}
